ms2

### 2017-08-30 ms2/ms2_display.Rmd
ms2 display

@@

>>>>

```{r ineq_hist}
cbbPalette <- c("#000000", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

ineq_table %>%
  filter(unit_type=='state') %>%
  # sum across units
  group_by(year, drug_group, n_claims) %>%
  summarize(n_bene=sum(n_bene)) %>%
  ungroup() %>%
  # compute the number of claims made by people making 1 claim, etc.
  mutate(n_class_claims = n_claims * n_bene) %>%
  # compute percentages: fr. of benes w/ 1 claim, fr. of claims made by 1-claimers, etc.
  group_by(year, drug_group) %>%
  mutate(pct_bene=pct(n_bene/sum(n_bene))) %>%
  select(year, drug_group, n_claims, pct_bene) %>%
  # group 3+ claims into one group, then sum up fractions in that new group
  mutate(n_claims=fct_other(factor(n_claims), keep=0:2, other_level='3+')) %>%
  group_by(year, drug_group, n_claims) %>%
  summarize_at(vars(pct_bene), sum) %>%
  ungroup() %>%
  # show only 2011 data
  filter(year==2011) %>%
  mutate(drug_group=fct_reorder(drug_group, pct_bene, fun=max)) %>%
  ggplot(aes(x=n_claims, y=pct_bene, fill=drug_group)) +
  geom_bar(stat='identity', position='dodge') +
  scale_fill_manual(values=cbbPalette) +
  theme_minimal()
```

@@

```{r linear_beta}
results %>%
  filter(unit_type=='hrr', model %in% c('univariate_fnz', 'univariate_fnz_beta'), term=='fnz') %>%
  select(bug, drug_group, model, estimate, p.value) %>%
  group_by(model) %>%
  mutate(p.value = p.adjust(p.value, method='BH')) %>%
  ungroup() %>%
  ggplot(aes(x=estimate, y=-log10(p.value), color=model, group=interaction(bug, drug_group))) +
  geom_hline(yintercept = -log10(0.05)) +
  geom_point() +
  geom_line(color='gray')
```
